---
title: "Assignment A1"
author: "ANLY 503"
date: "Due Friday September 4, 11:59pm"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source(here::here('00','randomize_roster.R'))
dsets <- c('cars2018.csv', 'clinical_data_breast_cancer_modified.csv',
           'sydneybeaches3.csv', 'gapminder.csv','Dataset_spine.csv')
```
  
## Instructions

Each student will be assigned a dataset based on the allocation
table below. All the datasets will be in CSV format and can be opened in Excel or in a text editor. 

Open and explore your dataset and **draw** 3 conceptual data visualizations to describe different aspects of the data set, stating in each case the question you want to address with the visualization. 
These should be **hand drawings**, but with enough detail (labels, shading, etc) to make the visualization clear to the reader. 

Submit **PDF or PNG file(s)** that contain scans or photos of your
concept drawings.

## Dataset allocation

```{r}
out <- roster_randomize(roster, dsets)
out1 <- split(out, out$assign)
out1 %>% map(~mutate(., students = paste(sis_user_id, collapse=', '))) %>% 
  map(~select(., students) %>% distinct()) %>% 
  bind_rows(.id = 'dataset') %>% 
  knitr::kable()
# dknitr::kable(out)
```

## Description of data sets

```{r}
tibble::tribble(~Data, ~Description,
                'cars2020.csv', 'A data set of fuel efficiency of cars available in the US in model year 2018',
                'clinical_data_breast_cancer_modified.csv', 'A data set of characteristics of breast cancer patients. Interesting variables include ER, PR and HER2 status which help guide treatment, tumor stage and grade, and vital status (dead or alive)',
                'sydneybeaches3.csv', 'Data on temperature, rainfall and bacterial (enterococci) concentrations at beaches in Sydney, Australia in 2013-2018',
                'gapminder.csv', 'The famous gapminder dataset of population, life expectancy and GDP in different countries over a period of 50 years',
                'Dataset_spine.csv', 'A dataset including normal and abnormal patients along with measures of cervical, thoracic and sacral spine and pelvic movement') %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()
```


