---
title: "Interactive Visualizations with Highchart in R"
output: 
    html_document:
        number_sections: true
        toc: true
        theme: cosmo
        highlight: tango
        code_folding: hide
---

```{r}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)

```


# Libraries
```{r}
library(tidyverse) #data Manipulation
library(highcharter) #interactive visualization
```

# Reading Input dataset and Summary of it


```{r}
#https://bigdatateaching.blob.core.windows.net/public/survey_results_public.csv
survey18 <- read_csv("https://bigdatateaching.blob.core.windows.net/public/survey_results_public.csv")
#glimpse(survey18)
```

# Philosophy 

This Kernel is purely aimed at helping a beginner with Interactive Visualizations using `highcharter` package in R.

# About highcharter

`highcharter` R package is a wrapper for the 'Highcharts' library including shortcut functions to plot R objects. 'Highcharts' <http://www.highcharts.com/> is a charting library offering numerous chart types with a simple configuration syntax.

# API

`highcharter` lets you plot using two different functions:

+ highchart()
+ hchart()

## highchart()

This function creates a Highchart chart using htmlwidgets. The widget can be rendered on HTML
pages generated from R Markdown, Shiny, or other applications. If you are familiar with ``ggplot2`` package, this function is very similar to `ggplot()` of the package where a base ggplot object is defined upon which further geometric layers can be added. 

Similarly, Once the `highchart()` function is defined further highchart elements can be added on top of it.

## hchart()

`hchart()` is a generic function to draw different charts on the fly.  The resulting chart is a highchart object so you can keep modifying with the implmented API. If you are familiar with ``ggplot2``, this function is similar to `qplot()` of it. 


Let us begin our Interactive Visualization journey with the easy plots.

# Icons Plot


```{r}
survey18 %>% 
  select(Gender) %>% 
  filter(!is.na(Gender)) %>% 
  filter(Gender %in% c('Male','Female')) %>% 
  count(Gender) %>% 
  mutate(perc = round((n /sum(n))*100)) -> gender_icons
  hciconarray(c('Female','Male'),gender_icons$perc,icons = c('male','female'))
```

# Bar

## hchart - column

Barplot is useful when you have comparable Categorical variables (factors). Let us look at what Years of Coding experience the respondents have got.  


```{r}
survey18 %>% 
  count(YearsCoding) %>% 
  hchart('column', hcaes(x = 'YearsCoding', y = 'n'))
```

As you can see in the above code, the chart type here is `column` that makes a vertical bar plot. Aesthetics are given using `hcaes()` (similar to `aes()` of `ggplot2`). 

## hchart - bar

Let us look at what people are hoping for five years. 

```{r}
survey18 %>% 
  count(HopeFiveYears) %>% 
  hchart('column', hcaes(x = 'HopeFiveYears', y = 'n'))
```

while the same column plot as above does the job, it can seen the large axis label have to be rotated and also cut - which may not be something fine always. Hence we will rotate the plot to make it a horizontal bar plot so large axis label can be accomodated. 



```{r}
survey18 %>% 
  count(HopeFiveYears) %>% 
  hchart('bar', hcaes(x = 'HopeFiveYears', y = 'n'))
```

The chart type here is `bar`. 


## Grouped Bar

Let us try to add one more dimension to our existing bar, by seeing how this hope for next five years varies based on their employement type.

```{r}
survey18 %>% 
  count(Employment, HopeFiveYears) %>% 
  hchart('bar', hcaes(x = 'HopeFiveYears', y = 'n', group = 'Employment'))
```

Now, this chart is as same as the above one except with the addition of grouped by Employement type. 

But the grouping can be flipped to see the story from a different lens.

```{r}
survey18 %>% 
  count(Employment, HopeFiveYears) %>% 
  hchart('bar', hcaes(x = 'Employment', y = 'n', group = 'HopeFiveYears'))
```


# Line & Area


## Line

Line is particularly prefered when you have Time variable in x-axis but considering we don't have any Time variable in the given dataset, we can chart out categorical varaibles using Line graph.

```{r}
survey18 %>% 
  count(YearsCoding) %>% 
  hchart('line', hcaes(x = 'YearsCoding', y = 'n'))
```

## Grouped Line


```{r}
survey18 %>% 
  count(YearsCoding, Employment) %>% 
  hchart('line', hcaes(x = 'YearsCoding', y = 'n', group = "Employment"))
```

## Spline

Line with Polynomial Interpolation.

```{r}
survey18 %>% 
  count(YearsCoding) %>% 
  hchart('spline', hcaes(x = 'YearsCoding', y = 'n'))
```


## Grouped Spline


```{r}
survey18 %>% 
  count(YearsCoding, Employment) %>% 
  hchart('spline', hcaes(x = 'YearsCoding', y = 'n', group = "Employment"))
```


## Area

```{r}
survey18 %>% 
  count(YearsCoding) %>% 
  hchart('area', hcaes(x = 'YearsCoding', y = 'n'))
```

## Grouped Area


```{r}
survey18 %>% 
  count(YearsCoding, Employment) %>% 
  hchart('area', hcaes(x = 'YearsCoding', y = 'n', group = "Employment"))
```

## Area Spline

```{r}
survey18 %>% 
  count(YearsCoding) %>% 
  hchart('areaspline', hcaes(x = 'YearsCoding', y = 'n'))
```

## Grouped Area Spline


```{r}
survey18 %>% 
  count(YearsCoding, Employment) %>% 
  hchart('areaspline', hcaes(x = 'YearsCoding', y = 'n', group = "Employment"))
```


As you can see in all the above plots, it's just the chart type changes and yet for the same data `hchart()` function is capable of managing to plot a different chart with the same data which makes this package really an easy way to make plots. 

# Scatter Plot

```{r}
survey18 %>% 
  filter(!is.na(Gender),
         Gender %in% c('Male','Female')) %>% 
  filter(Country %in% 'United Kingdom') %>% 
  filter(!is.na(Age),
         !is.na(ConvertedSalary),
         ConvertedSalary > 0) %>% 
  select(Gender, Country, Age, ConvertedSalary) %>% 
  mutate(age_grp = parse_number(Age)) %>%
  hchart('scatter',hcaes('ConvertedSalary',"age_grp")) 
  
```

# Treemap

## Boring 

```{r}
survey18 %>% 
  filter(!is.na(Age)) %>% 
  count(Age) %>% 
  hchart('treemap', hcaes(x = 'Age', value = 'n', color = 'n')) 

```

## Less Boring


```{r}
survey18 %>% 
  filter(!is.na(Age)) %>% 
  count(Age) %>% 
  hchart('treemap', hcaes(x = 'Age', value = 'n', color = 'n')) %>% 
    hc_colorAxis(stops = color_stops(colors = viridis::inferno(10)))

```


# highchart() Type Charts

## Bar

Most of the charts above can reproduced using the other method of `highchart()` and building layers on top of it. To start with, we will explain how we can build a bar chart like that.

```{r}

survey18 %>% 
  filter(!is.na(Gender)) %>% 
  filter(Gender %in% c('Male','Female')) %>% 
  count(Gender) -> Gender

highchart() %>% 
  hc_chart(type ="column") %>%
  hc_xAxis(categories = Gender$Gender) %>% 
  hc_add_series(data = Gender$n, name = "Gender")
```

## 3D-Bar 


```{r}
highchart() %>% 
  hc_chart(type ="column",
           options3d = list(enabled = TRUE, beta = 15, alpha = 15)) %>%
  hc_xAxis(categories = Gender$Gender) %>% 
  hc_add_series(data = Gender$n, name = "Gender")
  
```

# Maps 


## Nice but boring and incomplete
```{r}
data(worldgeojson, package = "highcharter")

survey18 %>% 
  filter(!is.na(Country)) %>% 
  count(Country) -> countries

highchart() %>%
hc_add_series_map(worldgeojson, countries, value = "n", joinBy = c('name','Country'))  

```

## Colorful Map with Title and Subtitle - Complete

```{r}
data(worldgeojson, package = "highcharter")

survey18 %>% 
  filter(!is.na(Country)) %>% 
  count(Country) -> countries

highchart() %>%
hc_add_series_map(worldgeojson, countries, value = "n", joinBy = c('name','Country'))  %>% 
  #hc_colors(c("darkorange", "darkgray")) %>% 
    hc_colorAxis(stops = color_stops()) %>% 
    hc_title(text = "Countries in World Map") %>% 
    hc_subtitle(text = "This is beauty")

```

# Themes

`Highcharter` also lets you aesthetically improve your charts with many inbuilt themes with just one extra line of code. 

### 538

First the famous Five Thirty Eight Theme:

```{r}

survey18 %>% 
  filter(!is.na(Employment)) %>% 
  count(Employment) %>% 
  hchart('column',hcaes('Employment','n')) %>% 
  hc_title(text = "Employment Type") %>% 
  hc_subtitle(text = "Source: Stack Overflow Dev Survey") %>% 
  hc_add_theme(hc_theme_538())
```

### A dark theme


```{r}

survey18 %>% 
  filter(!is.na(Employment)) %>% 
  count(Employment) %>% 
  hchart('column',hcaes('Employment','n')) %>% 
  hc_title(text = "Employment Type") %>% 
  hc_subtitle(text = "Source: Stack Overflow Dev Survey") %>% hc_add_theme(hc_theme_flatdark())
```

### Chalk Theme


```{r}

survey18 %>% 
  filter(!is.na(Employment)) %>% 
  count(Employment) %>% 
  hchart('column',hcaes('Employment','n')) %>% 
  hc_title(text = "Employment Type") %>% 
  hc_subtitle(text = "Source: Stack Overflow Dev Survey") %>%  hc_add_theme(hc_theme_chalk())
```
